### 2022-03-04 02_paper/02_study/paper_methods.Rmd
update begleitschreiben

```{r demographicstable, echo = FALSE}

@@

The currently ongoing data collection already yielded data from *n* = `r length(demo.data$Group=="Expert")` experts and

*n* = r nrow(demo.data[demo.data$Group == "Novice",]) novices.

>>>>

```{r demographicstable}

@@

The currently ongoing data collection already yielded data from *n* = `r length(demo.data$Group[demo.data$Group == "Expert"])` experts and *n* = `r length(demo.data$Group[demo.data$Group == "Novice"])` novices.
